---
title: "Car price model Linear regression"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Predict the price of the car model with Linear regression
```{r include=FALSE}
library(stringr)
library(MASS)
library(car)
```


Load the data
```{r}
load("rda/carprice.rda")
str(carprice)
```

Convert categorical variables to factors
```{r}
carprice$symboling <-as.factor(carprice$symboling)
carprice$cylindernumber<-as.factor(carprice$cylindernumber)
carprice$enginetype <- as.factor(carprice$enginetype)
carprice$fuelsystem<-as.factor(carprice$fuelsystem)
carprice$fueltype<-as.factor(carprice$fueltype)
carprice$aspiration<-as.factor(carprice$aspiration)
carprice$doornumber<-as.factor(carprice$doornumber)
carprice$carbody <-as.factor(carprice$carbody)
carprice$drivewheel<-as.factor(carprice$drivewheel)
carprice$enginelocation <- as.factor(carprice$enginelocation)
```

Working on variable "carprice$CarName"
```{r}
summary(as.factor(carprice$CarName))
```

There are multiple levels in CarName. Reduce the variables by taking only the carCompany
```{r}
carprice$carCompany <-gsub("\\ .*", "", carprice$CarName)
str(carprice$carCompany)
carprice$carCompany <- as.factor(carprice$carCompany)
summary(carprice$carCompany)
```

```{r}
levels(carprice$carCompany)
levels(carprice$carCompany)[10] <- "mazda"
levels(carprice$carCompany)[14] <- "nissan"
levels(carprice$carCompany)[16] <- "porsche"
levels(carprice$carCompany)[21] <- "toyota"
levels(carprice$carCompany)[21] <- "volkswagen"
levels(carprice$carCompany)[23] <- "volkswagen"
levels(carprice$carCompany)
```

Check for missing values
```{r}
sum(is.na(carprice))
```

Check for duplicated data
```{r}
which(duplicated(carprice))
```

Create the dummy variables
```{r}
# For carCompany
dummy_1 <- data.frame(model.matrix( ~carCompany, data = carprice))
dummy_1<-dummy_1[,-1]

# For carbody
dummy_2 <- data.frame(model.matrix( ~carbody, data = carprice))
dummy_2<-dummy_2[,-1]

# Drivewheel 
dummy_3 <- data.frame(model.matrix( ~drivewheel, data = carprice))
dummy_3<-dummy_3[,-1]

#Engine type
dummy_4 <- data.frame(model.matrix( ~enginetype, data = carprice))
dummy_4<-dummy_4[,-1]

#cylindernumber
dummy_5 <- data.frame(model.matrix( ~cylindernumber, data = carprice))
dummy_5<-dummy_5[,-1]

# Fuelsystem
dummy_6 <- data.frame(model.matrix( ~fuelsystem, data = carprice))
dummy_6<-dummy_6[,-1]

# Symboling
dummy_7 <- data.frame(model.matrix( ~symboling, data = carprice))
dummy_7<-dummy_7[,-1]
```

Variable having 2 levels are replaced to 0&1 and converted to numeric
```{r}
# for fueltype
levels(carprice$fueltype)<-c(1,0)
# assigning 1 to diesel and 0 to gas
carprice$fueltype<- as.numeric(levels(carprice$fueltype))[carprice$fueltype]

# for aspiration
levels(carprice$aspiration)<-c(1,0)
# Assigning 1 to "std" and 0 to "turbo"
carprice$aspiration <- as.numeric(levels(carprice$aspiration))[carprice$aspiration]

# For doornumber
levels(carprice$doornumber)<-c(1,0)
# Assigning 1 if the number of doors is 4, and 0 if the number of doors is 2.
carprice$doornumber<- as.numeric(levels(carprice$doornumber))[carprice$doornumber]

# Enginelocation
levels(carprice$enginelocation)<-c(1,0)
# Assigning 1 if the engine is front and 0 if in rear
carprice$enginelocation<- as.numeric(levels(carprice$enginelocation))[carprice$enginelocation]
```

Combine the dummy variables and the numeric columns of carprice dataset
```{r}
carprice_1 <- cbind(carprice[ , c(1,4:6,9:14,17,19:26)], dummy_1,dummy_2,dummy_3,dummy_4,dummy_5,dummy_6, dummy_7)
```

Modeling
```{r}
# Divide you data in 70:30 and create test and train datasets

set.seed(100)
indices= sample(1:nrow(carprice_1), 0.7*nrow(carprice_1))

train=carprice_1[indices,]
test = carprice_1[-indices,]
```

```{r}
model_1 <-lm(price~.,data=train[,-1])
summary(model_1)
```

Applying stepwise approach with step <- stepAIC(model_1, direction="both")
```{r include=FALSE}
step <- stepAIC(model_1, direction="both")
```

```{r}
step
```


```{r include=FALSE}
model_2 <- lm(formula = price ~ aspiration + enginelocation + carlength + 
                 carwidth + curbweight + enginesize + stroke + peakrpm + citympg + 
                 carCompanybmw + carCompanybuick + carCompanydodge + carCompanyhonda + 
                 carCompanyjaguar + carCompanymazda + carCompanymercury + 
                 carCompanymitsubishi + carCompanynissan + carCompanypeugeot + 
                 carCompanyplymouth + carCompanyporsche + carCompanyrenault + 
                 carCompanysaab + carCompanysubaru + carCompanytoyota + carCompanyvolkswagen + 
                 carbodyhardtop + carbodyhatchback + carbodysedan + carbodywagon + 
                 drivewheelrwd + enginetypeohc + enginetyperotor + cylindernumberfive + 
                 fuelsystem2bbl + fuelsystemmpfi + symboling.1 + symboling0 + 
                 symboling3, data = train[, -1])
summary(model_2)
vif(model_2)
```

Variables with high VIF and is insignificant are removed one by one

Removing carlength
```{r include=FALSE}
model_3 <- lm(formula = price ~ aspiration + enginelocation + 
                 carwidth + curbweight + enginesize + stroke + peakrpm + citympg + 
                 carCompanybmw + carCompanybuick + carCompanydodge + carCompanyhonda + 
                 carCompanyjaguar + carCompanymazda + carCompanymercury + 
                 carCompanymitsubishi + carCompanynissan + carCompanypeugeot + 
                 carCompanyplymouth + carCompanyporsche + carCompanyrenault + 
                 carCompanysaab + carCompanysubaru + carCompanytoyota + carCompanyvolkswagen + 
                 carbodyhardtop + carbodyhatchback + carbodysedan + carbodywagon + 
                 drivewheelrwd + enginetypeohc + enginetyperotor + cylindernumberfive + 
                 fuelsystem2bbl + fuelsystemmpfi + symboling.1 + symboling0 + 
                 symboling3, data = train[, -1])
summary(model_3)
vif(model_3)
```

Remove citympg
```{r include=FALSE}
model_4 <- lm(formula = price ~ aspiration + enginelocation + 
                 carwidth + curbweight + enginesize + stroke + peakrpm + 
                 carCompanybmw + carCompanybuick + carCompanydodge + carCompanyhonda + 
                 carCompanyjaguar + carCompanymazda + carCompanymercury + 
                 carCompanymitsubishi + carCompanynissan + carCompanypeugeot + 
                 carCompanyplymouth + carCompanyporsche + carCompanyrenault + 
                 carCompanysaab + carCompanysubaru + carCompanytoyota + carCompanyvolkswagen + 
                 carbodyhardtop + carbodyhatchback + carbodysedan + carbodywagon + 
                 drivewheelrwd + enginetypeohc + enginetyperotor + cylindernumberfive + 
                 fuelsystem2bbl + fuelsystemmpfi + symboling.1 + symboling0 + 
                 symboling3, data = train[, -1])
summary(model_4)
vif(model_4)
```


Remove fuelsystemmpfi
```{r include=FALSE}
model_5 <- lm(formula = price ~ aspiration + enginelocation + 
                 carwidth + curbweight + enginesize + stroke + peakrpm + 
                 carCompanybmw + carCompanybuick + carCompanydodge + carCompanyhonda + 
                 carCompanyjaguar + carCompanymazda + carCompanymercury + 
                 carCompanymitsubishi + carCompanynissan + carCompanypeugeot + 
                 carCompanyplymouth + carCompanyporsche + carCompanyrenault + 
                 carCompanysaab + carCompanysubaru + carCompanytoyota + carCompanyvolkswagen + 
                 carbodyhardtop + carbodyhatchback + carbodysedan + carbodywagon + 
                 drivewheelrwd + enginetypeohc + enginetyperotor + cylindernumberfive + 
                 fuelsystem2bbl + symboling.1 + symboling0 + 
                 symboling3, data = train[, -1])
summary(model_5)
vif(model_5)
```

Remove carcompanyporsche
```{r include=FALSE}
model_6 <- lm(formula = price ~ aspiration + enginelocation + 
                 carwidth + curbweight + enginesize + stroke + peakrpm + 
                 carCompanybmw + carCompanybuick + carCompanydodge + carCompanyhonda + 
                 carCompanyjaguar + carCompanymazda + carCompanymercury + 
                 carCompanymitsubishi + carCompanynissan + carCompanypeugeot + 
                 carCompanyplymouth + carCompanyrenault + 
                 carCompanysaab + carCompanysubaru + carCompanytoyota + carCompanyvolkswagen + 
                 carbodyhardtop + carbodyhatchback + carbodysedan + carbodywagon + 
                 drivewheelrwd + enginetypeohc + enginetyperotor + cylindernumberfive + 
                 fuelsystem2bbl + symboling.1 + symboling0 + 
                 symboling3, data = train[, -1])
summary(model_6)
vif(model_6)
```

Remove fuelsystem2bbl
```{r include=FALSE}
model_7 <- lm(formula = price ~ aspiration + enginelocation + 
                 carwidth + curbweight + enginesize + stroke + peakrpm + 
                 carCompanybmw + carCompanybuick + carCompanydodge + carCompanyhonda + 
                 carCompanyjaguar + carCompanymazda + carCompanymercury + 
                 carCompanymitsubishi + carCompanynissan + carCompanypeugeot + 
                 carCompanyplymouth + carCompanyrenault + 
                 carCompanysaab + carCompanysubaru + carCompanytoyota + carCompanyvolkswagen + 
                 carbodyhardtop + carbodyhatchback + carbodysedan + carbodywagon + 
                 drivewheelrwd + enginetypeohc + enginetyperotor + cylindernumberfive + 
                 symboling.1 + symboling0 + 
                 symboling3, data = train[, -1])
summary(model_7)
vif(model_7)
```

Remove symboling0
```{r include=FALSE}
model_8 <- lm(formula = price ~ aspiration + enginelocation + 
                 carwidth + curbweight + enginesize + stroke + peakrpm + 
                 carCompanybmw + carCompanybuick + carCompanydodge + carCompanyhonda + 
                 carCompanyjaguar + carCompanymazda + carCompanymercury + 
                 carCompanymitsubishi + carCompanynissan + carCompanypeugeot + 
                 carCompanyplymouth + carCompanyrenault + 
                 carCompanysaab + carCompanysubaru + carCompanytoyota + carCompanyvolkswagen + 
                 carbodyhardtop + carbodyhatchback + carbodysedan + carbodywagon + 
                 drivewheelrwd + enginetypeohc + enginetyperotor + cylindernumberfive + 
                 symboling.1 + symboling3, data = train[, -1])
summary(model_8)
vif(model_8)
```

Remove symboling.1
```{r include=FALSE}
model_9 <- lm(formula = price ~ aspiration + enginelocation + 
                 carwidth + curbweight + enginesize + stroke + peakrpm + 
                 carCompanybmw + carCompanybuick + carCompanydodge + carCompanyhonda + 
                 carCompanyjaguar + carCompanymazda + carCompanymercury + 
                 carCompanymitsubishi + carCompanynissan + carCompanypeugeot + 
                 carCompanyplymouth + carCompanyrenault + 
                 carCompanysaab + carCompanysubaru + carCompanytoyota + carCompanyvolkswagen + 
                 carbodyhardtop + carbodyhatchback + carbodysedan + carbodywagon + 
                 drivewheelrwd + enginetypeohc + enginetyperotor + cylindernumberfive + 
                 symboling3, data = train[, -1])
summary(model_9)
vif(model_9)
```

Remove carcompanymercury
```{r include=FALSE}
model_10 <- lm(formula = price ~ aspiration + enginelocation + 
                  carwidth + curbweight + enginesize + stroke + peakrpm + 
                  carCompanybmw + carCompanybuick + carCompanydodge + carCompanyhonda + 
                  carCompanyjaguar + carCompanymazda +
                  carCompanymitsubishi + carCompanynissan + carCompanypeugeot + 
                  carCompanyplymouth + carCompanyrenault + 
                  carCompanysaab + carCompanysubaru + carCompanytoyota + carCompanyvolkswagen + 
                  carbodyhardtop + carbodyhatchback + carbodysedan + carbodywagon + 
                  drivewheelrwd + enginetypeohc + enginetyperotor + cylindernumberfive + 
                  symboling3, data = train[, -1])
summary(model_10)
vif(model_10)
```

Remove symboling3
```{r include=FALSE}
model_11 <- lm(formula = price ~ aspiration + enginelocation + 
                  carwidth + curbweight + enginesize + stroke + peakrpm + 
                  carCompanybmw + carCompanybuick + carCompanydodge + carCompanyhonda + 
                  carCompanyjaguar + carCompanymazda +
                  carCompanymitsubishi + carCompanynissan + carCompanypeugeot + 
                  carCompanyplymouth + carCompanyrenault + 
                  carCompanysaab + carCompanysubaru + carCompanytoyota + carCompanyvolkswagen + 
                  carbodyhardtop + carbodyhatchback + carbodysedan + carbodywagon + 
                  drivewheelrwd + enginetypeohc + enginetyperotor + cylindernumberfive, data = train[, -1])
summary(model_11)
vif(model_11)
```

Remove carbodyhardtop
```{r include=FALSE}
model_12 <- lm(formula = price ~ aspiration + enginelocation + 
                  carwidth + curbweight + enginesize + stroke + peakrpm + 
                  carCompanybmw + carCompanybuick + carCompanydodge + carCompanyhonda + 
                  carCompanyjaguar + carCompanymazda +
                  carCompanymitsubishi + carCompanynissan + carCompanypeugeot + 
                  carCompanyplymouth + carCompanyrenault + 
                  carCompanysaab + carCompanysubaru + carCompanytoyota + carCompanyvolkswagen + 
                  carbodyhatchback + carbodysedan + carbodywagon + 
                  drivewheelrwd + enginetypeohc + enginetyperotor + cylindernumberfive, data = train[, -1])
summary(model_12)
vif(model_12)
```

Remove carbodyhatchback
```{r include=FALSE}
model_13 <- lm(formula = price ~ aspiration + enginelocation + 
                  carwidth + curbweight + enginesize + stroke + peakrpm + 
                  carCompanybmw + carCompanybuick + carCompanydodge + carCompanyhonda + 
                  carCompanyjaguar + carCompanymazda +
                  carCompanymitsubishi + carCompanynissan + carCompanypeugeot + 
                  carCompanyplymouth + carCompanyrenault + 
                  carCompanysaab + carCompanysubaru + carCompanytoyota + carCompanyvolkswagen + 
                  carbodysedan + carbodywagon + 
                  drivewheelrwd + enginetypeohc + enginetyperotor + cylindernumberfive, data = train[, -1])
summary(model_13)
vif(model_13)
```

Remove carbodysedan
```{r include=FALSE}
model_14 <- lm(formula = price ~ aspiration + enginelocation + 
                  carwidth + curbweight + enginesize + stroke + peakrpm + 
                  carCompanybmw + carCompanybuick + carCompanydodge + carCompanyhonda + 
                  carCompanyjaguar + carCompanymazda +
                  carCompanymitsubishi + carCompanynissan + carCompanypeugeot + 
                  carCompanyplymouth + carCompanyrenault + 
                  carCompanysaab + carCompanysubaru + carCompanytoyota + carCompanyvolkswagen + 
                  carbodywagon + 
                  drivewheelrwd + enginetypeohc + enginetyperotor + cylindernumberfive, data = train[, -1])
summary(model_14)
vif(model_14)
```

Remove carbodywagon
```{r include=FALSE}
model_15 <- lm(formula = price ~ aspiration + enginelocation + 
                  carwidth + curbweight + enginesize + stroke + peakrpm + 
                  carCompanybmw + carCompanybuick + carCompanydodge + carCompanyhonda + 
                  carCompanyjaguar + carCompanymazda +
                  carCompanymitsubishi + carCompanynissan + carCompanypeugeot + 
                  carCompanyplymouth + carCompanyrenault + 
                  carCompanysaab + carCompanysubaru + carCompanytoyota + carCompanyvolkswagen +
                  drivewheelrwd + enginetypeohc + enginetyperotor + cylindernumberfive, data = train[, -1])
summary(model_15)
vif(model_15)
```

All variables are significant now. Variable curbweight and enginesize have high VIFs. curbweight is very less significant as compared to enginesize

Remove curbweight
```{r include=FALSE}
model_16 <- lm(formula = price ~ aspiration + enginelocation + 
                  carwidth + enginesize + stroke + peakrpm + 
                  carCompanybmw + carCompanybuick + carCompanydodge + carCompanyhonda + 
                  carCompanyjaguar + carCompanymazda +
                  carCompanymitsubishi + carCompanynissan + carCompanypeugeot + 
                  carCompanyplymouth + carCompanyrenault + 
                  carCompanysaab + carCompanysubaru + carCompanytoyota + carCompanyvolkswagen +
                  drivewheelrwd + enginetypeohc + enginetyperotor + cylindernumberfive, data = train[, -1])
summary(model_16)
vif(model_16)
```

Remove cylindernumberfive
```{r include=FALSE}
model_17 <- lm(formula = price ~ aspiration + enginelocation + 
                  carwidth + enginesize + stroke + peakrpm + 
                  carCompanybmw + carCompanybuick + carCompanydodge + carCompanyhonda + 
                  carCompanyjaguar + carCompanymazda +
                  carCompanymitsubishi + carCompanynissan + carCompanypeugeot + 
                  carCompanyplymouth + carCompanyrenault + 
                  carCompanysaab + carCompanysubaru + carCompanytoyota + carCompanyvolkswagen +
                  drivewheelrwd + enginetypeohc + enginetyperotor, data = train[, -1])
summary(model_17)
vif(model_17)
```

Remove peakrpm (higher VIF, higher p-value as compared to othe variables in model)
```{r include=FALSE}
model_18 <- lm(formula = price ~ aspiration + enginelocation + 
                  carwidth + enginesize + stroke +  
                  carCompanybmw + carCompanybuick + carCompanydodge + carCompanyhonda + 
                  carCompanyjaguar + carCompanymazda +
                  carCompanymitsubishi + carCompanynissan + carCompanypeugeot + 
                  carCompanyplymouth + carCompanyrenault + 
                  carCompanysaab + carCompanysubaru + carCompanytoyota + carCompanyvolkswagen +
                  drivewheelrwd + enginetypeohc + enginetyperotor, data = train[, -1])
summary(model_18)
vif(model_18)
```

Remove carCompanysaab
```{r include=FALSE}
model_19 <- lm(formula = price ~ aspiration + enginelocation + 
                  carwidth + enginesize + stroke +  
                  carCompanybmw + carCompanybuick + carCompanydodge + carCompanyhonda + 
                  carCompanyjaguar + carCompanymazda +
                  carCompanymitsubishi + carCompanynissan + carCompanypeugeot + 
                  carCompanyplymouth + carCompanyrenault + 
                  carCompanysubaru + carCompanytoyota + carCompanyvolkswagen +
                  drivewheelrwd + enginetypeohc + enginetyperotor, data = train[, -1])
summary(model_19)
vif(model_19)
```

Remove carcompanyhonda
```{r include=FALSE}
model_20 <- lm(formula = price ~ aspiration + enginelocation + 
                  carwidth + enginesize + stroke +  
                  carCompanybmw + carCompanybuick + carCompanydodge + 
                  carCompanyjaguar + carCompanymazda +
                  carCompanymitsubishi + carCompanynissan + carCompanypeugeot + 
                  carCompanyplymouth + carCompanyrenault + 
                  carCompanysubaru + carCompanytoyota + carCompanyvolkswagen +
                  drivewheelrwd + enginetypeohc + enginetyperotor, data = train[, -1])
summary(model_20)
vif(model_20)
```

Remove carCompany renault
```{r include=FALSE}
model_21 <- lm(formula = price ~ aspiration + enginelocation + 
                  carwidth + enginesize + stroke +  
                  carCompanybmw + carCompanybuick + carCompanydodge + 
                  carCompanyjaguar + carCompanymazda +
                  carCompanymitsubishi + carCompanynissan + carCompanypeugeot + 
                  carCompanyplymouth + 
                  carCompanysubaru + carCompanytoyota + carCompanyvolkswagen +
                  drivewheelrwd + enginetypeohc + enginetyperotor, data = train[, -1])
summary(model_21)
vif(model_21)
```

Remove drivewheelrwd
```{r include=FALSE}
model_22 <- lm(formula = price ~ aspiration + enginelocation + 
                  carwidth + enginesize + stroke +  
                  carCompanybmw + carCompanybuick + carCompanydodge + 
                  carCompanyjaguar + carCompanymazda +
                  carCompanymitsubishi + carCompanynissan + carCompanypeugeot + 
                  carCompanyplymouth + 
                  carCompanysubaru + carCompanytoyota + carCompanyvolkswagen +
                  enginetypeohc + enginetyperotor, data = train[, -1])
summary(model_22)
vif(model_22)
```

Remove carCompanyvolkswagen
```{r include=FALSE}
model_23 <- lm(formula = price ~ aspiration + enginelocation + 
                  carwidth + enginesize + stroke +  
                  carCompanybmw + carCompanybuick + carCompanydodge + 
                  carCompanyjaguar + carCompanymazda +
                  carCompanymitsubishi + carCompanynissan + carCompanypeugeot + 
                  carCompanyplymouth + 
                  carCompanysubaru + carCompanytoyota + 
                  enginetypeohc + enginetyperotor, data = train[, -1])
summary(model_23)
vif(model_23)
```

Remove carCompanydodge
```{r include=FALSE}
model_24 <- lm(formula = price ~ aspiration + enginelocation + 
                  carwidth + enginesize + stroke +  
                  carCompanybmw + carCompanybuick + 
                  carCompanyjaguar + carCompanymazda +
                  carCompanymitsubishi + carCompanynissan + carCompanypeugeot + 
                  carCompanyplymouth + 
                  carCompanysubaru + carCompanytoyota + 
                  enginetypeohc + enginetyperotor, data = train[, -1])
summary(model_24)
vif(model_24)
```

Remove carCompanyplymouth
```{r include=FALSE}
model_25 <- lm(formula = price ~ aspiration + enginelocation + 
                  carwidth + enginesize + stroke +  
                  carCompanybmw + carCompanybuick + 
                  carCompanyjaguar + carCompanymazda +
                  carCompanymitsubishi + carCompanynissan + carCompanypeugeot + 
                  carCompanysubaru + carCompanytoyota + 
                  enginetypeohc + enginetyperotor, data = train[, -1])
summary(model_25)
vif(model_25)
```

Remove carCompanynissan
```{r include=FALSE}
model_26 <- lm(formula = price ~ aspiration + enginelocation + 
                  carwidth + enginesize + stroke +  
                  carCompanybmw + carCompanybuick + 
                  carCompanyjaguar + carCompanymazda +
                  carCompanymitsubishi + carCompanypeugeot + 
                  carCompanysubaru + carCompanytoyota + 
                  enginetypeohc + enginetyperotor, data = train[, -1])
summary(model_26)
vif(model_26)
```

Remove enginetypeohc
```{r include=FALSE}
model_27 <- lm(formula = price ~ aspiration + enginelocation + 
                  carwidth + enginesize + stroke +  
                  carCompanybmw + carCompanybuick + 
                  carCompanyjaguar + carCompanymazda +
                  carCompanymitsubishi + carCompanypeugeot + 
                  carCompanysubaru + carCompanytoyota + 
                  enginetyperotor, data = train[, -1])
summary(model_27)
vif(model_27)
```

Remove carCompanymitsubishi
```{r include=FALSE}
model_28 <- lm(formula = price ~ aspiration + enginelocation + 
                  carwidth + enginesize + stroke +  
                  carCompanybmw + carCompanybuick + 
                  carCompanyjaguar + carCompanypeugeot + 
                  carCompanysubaru + carCompanytoyota + 
                  enginetyperotor, data = train[, -1])
summary(model_28)
vif(model_28)
```

Remove carCompanytoyota
```{r include=FALSE}
model_29 <- lm(formula = price ~ aspiration + enginelocation + 
                  carwidth + enginesize + stroke +  
                  carCompanybmw + carCompanybuick + 
                  carCompanyjaguar + carCompanypeugeot + 
                  carCompanysubaru +  
                  enginetyperotor, data = train[, -1])
summary(model_29)
vif(model_29)
```

Remove carcompanyPeugeot
```{r include=FALSE}
model_30 <- lm(formula = price ~ aspiration + enginelocation + 
                  carwidth + enginesize + stroke +  
                  carCompanybmw + carCompanybuick + 
                  carCompanyjaguar + 
                  carCompanysubaru +  
                  enginetyperotor, data = train[, -1])
summary(model_30)
vif(model_30)
```

Adjusted R-squared = 0.9437. carwidth, enginesize have high VIF. Lets see what happens when these are removed.

Removing carwidth
```{r include=FALSE}
model_31a <- lm(formula = price ~ aspiration + enginelocation + 
                  enginesize + stroke +  
                  carCompanybmw + carCompanybuick + 
                  carCompanyjaguar + 
                  carCompanysubaru +  
                  enginetyperotor, data = train[, -1])
summary(model_31a)
vif(model_31a)
```

Adjusted R-squared decreased from 0.9437 to 0.9224, a decline of 2 percent.

Removing enginesize
```{r include=FALSE}
model_31b <- lm(formula = price ~ aspiration + enginelocation + 
                  carwidth + stroke +  
                  carCompanybmw + carCompanybuick + 
                  carCompanyjaguar + 
                  carCompanysubaru +  
                  enginetyperotor, data = train[, -1])
summary(model_31b)
vif(model_31b)
```

Adjusted R-squared decreases from 0.9437 to 0.8926. These are fairly large decreases.

Remove variables which are comparatively less significant

Remove aspiration
```{r include=FALSE}
model_31 <- lm(formula = price ~  enginelocation + 
                  carwidth + enginesize + stroke +  
                  carCompanybmw + carCompanybuick + 
                  carCompanyjaguar + 
                  carCompanysubaru +  
                  enginetyperotor, data = train[, -1])
summary(model_31)
vif(model_31)
```

Remove carcompanysubaru
```{r include=FALSE}
model_32 <- lm(formula = price ~  enginelocation + 
                  carwidth + enginesize + stroke +  
                  carCompanybmw + carCompanybuick + 
                  carCompanyjaguar + 
                  enginetyperotor, data = train[, -1])
summary(model_32)
vif(model_32)
```

Remove enginetyperotor
```{r include=FALSE}
model_33 <- lm(formula = price ~  enginelocation + 
                  carwidth + enginesize + stroke +  
                  carCompanybmw + carCompanybuick + 
                  carCompanyjaguar, data = train[, -1])
summary(model_33)
vif(model_33)
```

Remove stroke
```{r include=FALSE}
model_34 <- lm(formula = price ~  enginelocation + 
                  carwidth + enginesize +  
                  carCompanybmw + carCompanybuick + 
                  carCompanyjaguar, data = train[, -1])
summary(model_34)
vif(model_34)
```

Remove carcompany jaguar
```{r echo=TRUE}
model_35 <- lm(formula = price ~  enginelocation + 
                  carwidth + enginesize + 
                  carCompanybmw + carCompanybuick, data = train[, -1])
summary(model_35)
vif(model_35)
```

Now there are 5 variables in the model.

Test the model on test dataset
```{r}
Predict_1 <- predict(model_35,test[,-c(1,20)])
```

Add a new column "test_predict" into the test dataset
```{r}
test$test_price <- Predict_1
```

Calculate the test R2 
```{r}
cor(test$price,test$test_price)
cor(test$price,test$test_price)^2
```
